Dependent Object Types

### 2012-09-17 doc/fool/article.tex
clarif

Using lower bounds of $\Bot$ for the abstract type members ensures
they can vary covariantly. On the other hand, $\mi{choose}$ cannot be
called meaningfully, unless $A$ and $B$ have realizable lower bounds.

As expected, 
\begin{align*}
&{\mi{choices.Alt_c} \refine a {\Ldecl C \Bot {\mi{pets.Dog_c}}}}\\
\sub\gap&{\mi{choices.Alt_c} \refine a {\Ldecl C \Bot {\mi{pets.Pet_c}}}}
\end{align*}
but
\begin{align*}
&{\mi{choices.Alt_c} \refine a {\Ldecl C {\mi{pets.Dog_c}} {\mi{pets.Dog_c}}}}\\
\not\sub\gap&{\mi{choices.Alt_c} \refine a {\Ldecl C {\mi{pets.Pet_c}} {\mi{pets.Pet_c}}}}
\end{align*}

>>>>

Using lower bounds of $\Bot$ for the abstract type members means they
can vary covariantly. However, we wouldn't want to pass in any
${\mi{pets.Pet_c}}$ to a $\mi{choose}$ method that expects only a
${\mi{pets.Dog_c}}$. Therefore,
\begin{align*}
&{\mi{choices.Alt_c} \refine a {\Ldecl C \Bot {\mi{pets.Dog_c}}}}\\
\sub\gap&{\mi{choices.Alt_c} \refine a {\Ldecl C \Bot {\mi{pets.Pet_c}}}}
\end{align*}
but
\begin{align*}
&{\mi{choices.Alt_c} \refine a {\Ldecl C {\mi{pets.Dog_c}} {\mi{pets.Dog_c}}}}\\
\not\sub\gap&{\mi{choices.Alt_c} \refine a {\Ldecl C {\mi{pets.Pet_c}} {\mi{pets.Pet_c}}}}
\end{align*}

As expected, we cannot invoke $\mi{choose}$ meaningfully, unless $A$
and $B$ have realizable lower bounds. For example, assuming we refine
the types above so that $\Ldecl A C C$ and $\Ldecl B C C$, we cannot
invoke $\mi{choose}$ when $C$ has a lower bound of $\Bot$ but only
when it has a realizable lower bound such as $\mi{pets.Dog_c}$.
